Exception Handling Bug Hazards in Android

### 2015-10-07 SPRINGER_JOURNAL/msr_journal.tex
survey section

\begin{figure} \centering \includegraphics[scale=0.63]{charts/agree_new2.png}
\caption{How often developers throw and handle exceptions during app development.}
\label{fig:oftenhandle}
\end{figure}

\begin{figure} \centering \includegraphics[scale=0.57]{charts/yes_no_new2.png}
\caption{Summary of some survey question answers. }
\label{fig:oftenhandle}
\end{figure}

@@

Developers were asked to rank the main causes of crashes. Approximately 68\% of the repondents ranked the exceptions signaled by programming logic mistakes e.g. NullPointerExceptions as the Top 1 and Top 2 cause of crashes as illustrated in Figure ~\ref{figure:ranking}. In our mining study the exceptions signaled due to programming logic mistakes (java.lang and util) where the causes of 52,0\% of the exception stack traces found. Hence, the developers perspective is aligned with what was revealed in mining study.
%[width=.9\hsize]
\begin{figure*} 
\centering \includegraphics[scale=0.42]{charts/maincauses.png}
\caption{Developers perspectives on the main causes of crashes.}\label{fig:ranking} 
\end{figure*}

>>>>

\begin{figure} \centering \includegraphics[scale=0.60]{charts/agree_new2.png}
\caption{How often developers throw and handle exceptions during app development.}
\label{fig:oftenhandle}
\end{figure}

\begin{figure} \centering \includegraphics[scale=0.60]{charts/yes_no_new2.png}
\caption{Summary of some survey question answers. }
\label{fig:oftenhandle}
\end{figure}

@@

Developers were asked to rank the main causes of crashes. Approximately 68\% of the repondents ranked the exceptions signaled by programming logic mistakes e.g. NullPointerExceptions as the Top 1 and Top 2 cause of crashes as illustrated in Figure ~\ref{figure:ranking}. In our mining study the exceptions signaled due to programming logic mistakes (java.lang and util) where the causes of 52,0\% of the exception stack traces found. Hence, the developers perspective is aligned with what was revealed in mining study.
%[width=.9\hsize]
\begin{figure*} 
\centering \includegraphics[scale=0.60]{charts/ranking.png}
\caption{Developers perspectives on the main causes of crashes.}\label{fig:ranking} 
\end{figure*}
